---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# porter

<!-- badges: start -->
<!-- badges: end -->

The goal of {porter} is to generate port files for [rdyncall](https://github.com/hongyuanjia/rdyncall)
to support Foreign Function Interface (FFI) for C Libraries in R. It uses
[CastXML](https://github.com/CastXML/CastXML), a C-family abstract syntax tree
XML output tool to parse C header files.

## Installation

You can install porter from CRAN with:

``` r
install.packages("porter")
```

You can install the development version of porter from GitHub with:

``` r
remotes::install_github("hongyuanjia/porter")
```

## Example

### Locate CastXML

porter uses CastXML but does not download or install it. Install CastXML with
your system package manager before calling `port()`.

- On Windows, [Scoop](https://scoop.sh/) can install CastXML via
  `scoop install main/castxml`.
- On macOS, [Homebrew](https://brew.sh/) can install CastXML via
  `brew install castxml`.
- On Linux, use your distribution package manager when it provides CastXML, or
  use Linuxbrew via `brew install castxml`.

`locate_castxml()` returns the CastXML executable porter will use. By default it
checks `Sys.which("castxml")`, then common package-manager paths for Homebrew,
Linuxbrew, Scoop, Chocolatey, and conda. Set `options(porter.castxml = ...)` to
force a specific executable or installation directory.

```{r example, eval = FALSE}
library(porter)

locate_castxml()
#>                         0.7.0
#> "/opt/homebrew/bin/castxml"
```

### Generate port files for C libraries

Run `port()` with the path of a C header file:

```{r port}
library(porter)

header <- tempfile(fileext = ".h")
writeLines(c(
  "typedef struct Point { int x; double y; } Point;",
  "int add(int a, int b);",
  "int message(const char *fmt, ...);"
), header)

p <- port(header)

p <- port_set(p,
  Package = "Example",
  Version = "1.0",
  Library = "example"
)

p
```

Use `port_write()` to save the port file.

```{r write, eval = FALSE}
port_write(p, file.path(tempdir(), "Example.dynport"))
```

## Author

Hongyuan Jia

## License

The project is released under the terms of MIT License.

Copyright © 2023 Hongyuan Jia
