---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(porter)
```

# porter

<!-- badges: start -->
<!-- badges: end -->

The goal of {porter} is to generate port files for [rdyncall](https://github.com/hongyuanjia/rdyncall)
to support Foreign Function Interface (FFI) for C Libraries in R. It uses
[CastXML](https://github.com/CastXML/CastXML), a C-family abstract syntax tree
XML output tool to parse C header files.

## Installation

You can install the development version of porter like so:

``` r
remotes::install_github("hongyuanjia/port")
```

## Example

### Manage CastXML installation

You can use `install_castxml()` to install CastXML. It downloads the pre-built
binaries of CastXML together with the LLVM/Clang dependencies via the
[CastXML Superbuild](https://github.com/CastXML/CastXMLSuperbuild) project.

`locate_castxml()` will return the current CastXML in use:

```{r example, eval = FALSE}
install_castxml("latest")

locate_castxml()
#>                                         0.5.0
#> "C:\\Users\\hongy\\scoop\\shims\\castxml.exe"
```

Instead of using `install_castxml()`, you may directly use your package manager
to install CastXML, as it may already provide a `castxml` package.

- On Windows, you can use [Scoop](https://scoop.sh/) to install CastXML via:
  `scoop install main/castxml`
- On macOS, you can use [Homebrew](https://brew.sh/) to install CastXML via:
  `brew install castxml`
- On Linux, you can check if your system package manager provides CastXML or
  not via [Repology](https://repology.org/project/castxml/versions).

### Generate port files for C libraries

Take the [SDL2](https://www.libsdl.org/) library as an example. After
downloading the SDL2 [source](https://github.com/libsdl-org/SDL/releases), run
`port()` with the path of SDL2 header file (here `dir` is directory of SDL2
source):

```{r sdl2}
version <- "2.28.0"
dir <- file.path(tempdir(), paste0("SDL2-", version))
if (!dir.exists(dir)) {
  zipfile <- porter:::download_src_sdl2(version)
  unzip(zipfile, exdir = tempdir())
}
```

```{r port}
p <- port(file.path(dir, "include", "SDL.h"))

p <- port_set(p,
  Package = "SDL2",
  Version = "2.28.0",
  Library = c("SDL", "SDL-2.28", "SDL-2.28.so.0")
)

p
```

Use `port_write()` to save the port file.

```{r write}
port_write(p, file.path(tempdir(), "SDL2.dynport"))
```

## Author

Hongyuan Jia

## License

The project is released under the terms of MIT License.

Copyright © 2023 Hongyuan Jia
